\chapter{Technological frameworks}
\label{chap:techFrm}


% Provide a description of the technological frameworks used during the
% development phase of your product. Such technological frameworks
% should be properly introduced and described from the point of view of their
% use during the development of your product.

This chapter provides a description of the technological frameworks used during
the development phase of \textbf{iCrash} system.


\section{Java Programming Language}
\label{sec:Java}
%It was required to \ldots 
Java is a programming language. Java is general-purpose multi-paradigm, class-based language with high
portability of the software. Java is a high-level programming language
originally developed by Sun Microsystems and released in 1995. Java runs on a variety of platforms, 
such as Windows, Mac OS, and the various versions of UNIX. 

\section{MySQL}
\label{sec:MySQL}
 MySQ is an open-source relational database management system (RDBMS). MySQL is the world's 
 most popular open source database. With its proven performance, reliability, and ease-of-use, 
 MySQL has become the leading database choice for web-based applications, used by high profile 
 web properties including Facebook, Twitter, YouTube, and all five of the top five websites*. 
 Additionally, it is an extremely popular choice as embedded database, distributed by thousands 
 of ISVs and OEMs.

\section{Eclipse}
\label{sec:eclipse}
Eclipse is an integrated development environment (IDE) used in computer
programming, and is the most widely used Java IDE. It contains a base workspace and an 
extensible plug-in system for customizing the environment. Eclipse is
written mostly in Java and its primary use is for developing Java applications,
but it may also be used to develop applications in other programming languages.

\section{Git}
label{sec:Git}
Git is a version control system (VCS) for tracking changes in
computer files and coordinating work on those files among multiple people. 
It is primarily used for software development,but it can be used to keep 
track of changes in any files. As a distributed revision control system it 
is aimed at speed, data integrity, and support for distributed, non-linear workflows.

\section{LaTeX}
\label{sec:latex}
LaTeX is a document preparation system for high-quality typesetting. 
It is most often used for medium-to-large technical or scientific documents but it
 can be used for almost any form of publishing.
 
\section{Excalibur}
\label{sec:excalibur}

Excalibur is a tool supporting the Messir methodology, a Scientific Method for the Software 
Engineering Master, used in Software Engineering Lectures at bachelor and master levels.

Excalibur tool covers the phase of Requirements Analysis and its main features are 
requirements analysis specification (its own DSL), requirements report generation 
(latex/pdf) and requirements simulation (prolog). It relies on Eclipse technologies 
as XText for textual specification and Sirius for graphical views of the textual specifications

% \section{Tool 2}
% \label{sec:GUIDev}
% It was required to \ldots
% 


